---
title             : "EDLD 610: Lab 8"
shorttitle        : "Fall 2019"

author: 
  - name          : "Jim Wright"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "1655 Alder Street 
                     Eugene, OR 97401"
    email         : "jwrigh16@uoregon.edu"
  - name          : "Claire Zhang"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "University of Oregon Department of Communication Disorders & Sciences"
  - id            : "2"
    institution   : "University of Oregon Department of Educational Methodology, Policy, & Leadership"


abstract: |
  The purpose of this lab is to gain experience using the papaja package of rmd to render an APA style document.  The second purpose is to work collaboratively with others to practice the process of using GitKraken and GitHub to produce and share data.  
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "APA, papaja, GitKraken, GitHub, merge error"


bibliography      : lab_8_references.bib

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library(rio)
library(here)
library(tidyverse)
library(janitor)
library(datapasta)
library(papaja)
library(knitr)

theme_set(theme_minimal())
opts_chunk$set(echo = FALSE,
               fig.width = 6.5,
               fig.height = 8)

```

```{r load-data}
star <- import(here("data", "star.csv"),
            setclass = "tbl_df") %>% 
  characterize()

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction 

This introduction provides some examples of in-text citations discussed during week 5, lecture 2 [@broglio2014].  As discussed by Sohlberg and Ledbetter [-@sohlberg2016], I find it fascinating we can add APA references into R markdown. 

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

```{r tbls, results = "asis"}

?kable



library(kableExtra)

star %>% 
  group_by(sex, frl) %>% 
  summarize(math_mean = mean(tmathss),
            math_sd   = sd(tmathss),
            rdg_mean  = mean(treadss),
            rdg_sd    = sd(treadss)) %>% 
  kable(digits = 2)

```

The average reading and math scores were higher in males and females who did not qualify for free and reduced lunch (FRL), suggesting children who do qualify for free and reduced lunch may be vulnerable to decreased reading and math skills.  For both FRL groups (students who qualified and did not qualify for FRL), girls scored higher on average in both reading and math. 

```{r plot}

star %>% 
  mutate(`Lunch status` = ifelse(frl == "no", "Paid Meals", "Free/Reduced Price Meals")) %>% 
  ggplot(aes(totexp, tmathss)) +
  geom_point(color = "gray70") +
  geom_smooth(aes(color = `Lunch status`), 
              method = "lm",
              fill = "#8da0cb") +
  scale_color_brewer(palette = "Set2") +
  labs(y = "Total Math Scale Score",
       x = "Teacher Experience (years)",
       title = "Relation between teacher experience and math scores",
       subtitle = "Separate regression lines displayed by free/reduced price lunch status") +
 theme_minimal() +
 theme(legend.position = "bottom")

```

For both students who do and do not qualify for free and reduced lunch, there appears to be a slight, positve correlation between the student's total math scale score and the teacher's years of experience. Teachers with more years of experience are more likely to teach students who score higher in math than teachers with less years of experience. Overall, students who do not qualify for free and reduced lunch score higher in math than students who do qualify for free and reduced lunch regardless of the number of years the teacher has taught. 

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "lab_8_references.bib")

```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
