---
title             : "EDLD 610: Lab 8"
shorttitle        : "Fall 2019"

author: 
  - name          : "Jim Wright"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "1655 Alder Street 
                     Eugene, OR 97401"
    email         : "jwrigh16@uoregon.edu"
  - name          : "Claire Zhang"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "University of Oregon Department of Communication Disorders & Sciences"
  - id            : "2"
    institution   : "University of Oregon Department of Educational Methodology, Policy, & Leadership"


abstract: |
  The purpose of this lab is to gain experience using the papaja package of rmd to render an APA style document.  The second purpose is to work collaboratively with others to practice the process of using GitKraken and GitHub to produce and share data.  
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "APA, papaja, GitKraken, GitHub, merge error"


bibliography      : "lab_8_references.bib"

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library(rio)
library(here)
library(tidyverse)
library(janitor)
library(datapasta)
library(papaja)

theme_set(theme_minimal())
opts_chunk$set(echo = FALSE,
               fig.width = 6.5,
               fig.height = 8)

```

```{r load-data}
star <- import(here("data", "star.csv"),
            setclass = "tbl_df") %>% 
  characterize()

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction 

This introduction provides some examples of in-text citations discussed during week 5, lecture 2 [@Broglio_2014].  As discussed by [-@Sohlberg_2014], I find it fascinating we can add APA references into R markdown. 

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "lab_8_references.bib")

```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
